\def\sphoyear{2020}
\setcounter{section}{0}
% Headers and Descriptions
\fancyhead[L]{\textbf{SPhO \sphoyear}} \fancyhead[R]{\textbf{Questions}}


\begin{titlepage}
\centering

{\Huge\bfseries SPhO \sphoyear}

\vspace{1cm}

{\LARGE Problem Set}

\vspace{2cm}

{\Large Compiled by: Tan Chien Hao, \texttt{www.tchlabs.net}}

\vspace{2cm}

{\Large Edited/Proofread by: Keith Chan, Sun Yu Chieh}
%Collaborators please feel free to add on!

\vspace{2cm}

{\large Suggest changes at: \github}


\vfill

{\itshape Last edited: \today}
\end{titlepage}

\begin{problem}
    A cylindrical rod has a radius of \qty{1.0}{\cm} and length \qty{1.0}{\m}. It is made up of two sections, each of length \qty{0.5}{\m}. The material of one section is zinc and that of the other section is copper. The end of the rod made of zinc is pivoted to a fixed point O. The rod is first held so that it is horizontal and then released. Determine the angular velocity of the rod when it is in the vertical position. (Densities: zinc: \qty{7135}{\kg\m^{-3}}; copper: \qty{8940}{\kg\m^{-3}} \hfill $[10]$
\end{problem}

\begin{problem}
    \begin{subproblem}
        A student is sitting on a swing which is swinging back and forth with a constant angular amplitude of $45^{\circ}$. The length of the swing is 5 m. A loudspeaker, placed at a short distance away from the swing, produces a sound with a constant frequency of 400 Hz. What are the maximum and minimum frequency of the sound heard by the student? (Speed of sound waves = $\qty{330}{\m\s^{-1}}$) \hfill $[5]$
    \end{subproblem}
    \renewcommand{\theenumi}{(\alph{enumi})}
    \begin{subproblem}
        A compound microscope contains two thin lenses of focal length $\qty{6.0}{\mm}$ and $\qty{40.0}{\mm}$ respectively. The lenses are separated by a distance of $\qty{200}{\mm}$. The final image is formed $\qty{250}{\mm}$ away from the eye lens. Calculate
        \begin{enumerate}
            \item The distance of the object from the objective lens
            \item The magnifying power of the microscope. \hfill $[5]$
        \end{enumerate}
    \end{subproblem}
\end{problem}

\begin{problem}
    One end of a thin conducting rod of length $l$ is pivoted to a fixed point. The rod has a resistance of $R$ and its two ends of the rod are connected to a resistor with resistance $R_0$ The rod is rotating with a constant angular velocity $\omega$ in a uniform magnetic field of flux density $B$. This direction of magnetic field is normal to the plane of rotation of the rod.
    \renewcommand{\theenumi}{(\alph{enumi})}
    \begin{enumerate}
        \item What is the emf induced in the rod?
        \item Determine the electric power developed in the resistor.
        \item Describe, with evidence, the origin of the electric power developed in the resistor.
    \end{enumerate}
    \hfill $[10]$
\end{problem}

\begin{problem}
    A free electron collides with a hydrogen atom which is in the ground state. After the collision, the hydrogen atom is excited and during the process of de-excitation, two photons are emitted. The wavelength of one of the photons emitted is \qty{656.3}{\nm}. The electron, after the collision, has de Broglie wavelength of \qty{1.915}{\nm}.
    \renewcommand{\theenumi}{(\alph{enumi})}
    \begin{enumerate}
        \item What is the wavelength of the other photon emitted during the de-excitation?
        \item What is the speed of the free electron before collision? \hfill $[10]$
    \end{enumerate}
\end{problem}

\begin{problem}
    \begin{subproblem}
        An airplane flying horizontally with a constant speed of $540 \text{km h}^{-1}$ at a height of $1200 \text{m}$ fires a projectile horizontally in its direction of motion at a speed of $u \text{ m s}^{-1}$ relative to the plane. At this instant, a vehicle is at a point on the ground d km horizontally from the airplane. The vehicle is moving with a constant speed of $40 \text{m s}^{-1}$ on a horizontal road in the direction of motion of the plane. What must be the minimum value of d so that the projectile will hit the vehicle? If, at the instant when the projectile is fired, the value of d is 5 times its minimum value, what is the speed of the projectile when it hits the vehicle? [7]
    \end{subproblem}
\end{problem}